Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-12-19 cover-letter/refactor-letter.tex
Add transition paragraph to the AGREE background.

To aid in reviewing this new refactored manuscript, I am including here a detailed summary of the changes, and where possible, the submission itself indicates the changes directly to make it easier for the reviewers to inspect.
\begin{itemize}
  \item We rewrote the abstract to be active present tense, define the problem, approach, contributions, and results.
  \item We revised the introduction to pull in the last three paragraphs of section two, and to better funnel readers from the big picture, intuitive overview, to specific details on our tools and contributions. 
  \item We added is discussion section to the case study in section 8 to address lessons learned from our experience. We also enlarged significantly figures 14 and 17.
\end{itemize}

>>>>

To aid in reviewing this new refactored manuscript, I am including here a detailed summary of the changes, and where possible, the submission itself indicates the changes directly to make it easier for the reviewers to inspect.
\begin{itemize}
  \item We rewrote the abstract to be active present tense, define the problem, approach, contributions, and results.
  \item We revised the introduction to pull in the last three paragraphs of section two, and to better funnel readers from the big picture, intuitive overview, to specific details on our tools and contributions. 
  \item We added a discussion section to the case study in section 8 to address lessons learned from our experience. We also enlarged significantly figures 14 and 17.
  \item We added a paragraph to the end of the example section explaining that our discussion of AGREE early in the paper, of necessity, is a birdseye view of its role in the BriefCASE workflow for the reader that perhaps doesn't want all the detail in the following sections. The actual AGREE section of the paper then presents notation, semantics, and usage so that the reader is able to contextualize our primary contributions. We also added in that paragraph direct references to the sections in the paper where the detailed contracts for the example system are discussed. 
\end{itemize}

### 2022-12-19 paper/example.tex
Make figures bigger
Add transition paragraph to the AGREE background.

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{flowchart.png} \\
    \end{tabular}
  \end{center}
\caption{Simplified \brfcs\ workflow. Shaded portions are the focus of the present discussion.}
\label{fig:flowchart}
\end{figure*}

\begin{figure*}[h]
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{example.png}
    \end{tabular}
  \end{center}
\caption{Initial design for an automated UAV route planning system.}
\label{fig:example}
\end{figure*}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{example-certificate.png} \\
    \end{tabular}
  \end{center}
\caption{\agr\ failure certificate for initial design.}
\label{fig:example-certificate}
\end{figure}

@@

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.3]{hardened.png}
    \end{tabular}
  \end{center}
  \caption{Cyber-hardened design for an automated UAV route planning system}
  \label{fig:hardened}
\end{figure*}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.38]{agree-test-output.png} \\
      (a) \\ \\
      \includegraphics[scale=0.4]{hardened-certificate.png} \\
      (b)
    \end{tabular}
  \end{center}
  \caption{\agr\ verification certificates. (a) Test contract verification results. (b) Cyber-hardened design verification results.}
  \label{fig:hardened-certificate}
\end{figure}

@@

>>>>

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[width=0.8\textwidth]{flowchart.png} \\
    \end{tabular}
  \end{center}
\caption{Simplified \brfcs\ workflow. Shaded portions are the focus of the present discussion.}
\label{fig:flowchart}
\end{figure*}

\begin{figure*}[h]
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[width=\textwidth]{example.png}
    \end{tabular}
  \end{center}
\caption{Initial design for an automated UAV route planning system.}
\label{fig:example}
\end{figure*}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[width=1\columnwidth]{example-certificate.png} \\
    \end{tabular}
  \end{center}
\caption{\agr\ failure certificate for initial design.}
\label{fig:example-certificate}
\end{figure}

@@

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[width=2\columnwidth]{hardened.png}
    \end{tabular}
  \end{center}
  \caption{Cyber-hardened design for an automated UAV route planning system}
  \label{fig:hardened}
\end{figure*}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[width=\columnwidth]{agree-test-output.png} \\
      (a) \\ \\
      \includegraphics[width=\columnwidth]{hardened-certificate.png} \\
      (b)
    \end{tabular}
  \end{center}
  \caption{\agr\ verification certificates. (a) Test contract verification results. (b) Cyber-hardened design verification results.}
  \label{fig:hardened-certificate}
\end{figure}

@@

\newjunk{
Our discussion so far regarding the role of \agr\ in the \brfcs\ workflow in \figref{fig:flowchart} has been high-level and abstract. Indeed, we have only given a birdseye view of how \agr\ supports the verification of the system, code contracts, and test contracts, as well as how it provides the proof results that underpin our claim that the synthesized high-assurance components guarantee the \agr\ verification results. In the following sections we delve into the details of \agr, including its notation, semantics, and usage, to set the stage for our primary contributions in \secref{sec:code-contracts}, \secref{sec:testing}, and \secref{sec:synthesis}. For reference to where we discuss the actual contracts for the example system, \secref{sec:sw-contract} is the exposition of the \agr\ contract for the SW component, \secref{sec:ha-contracts} is the exposition of the code contracts for the high-assurance filter and monitor shown in \figref{fig:hardened}, and \secref{sec:testing} includes an exposition of a test contract for the monitor. 
}
